Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

>>>>

```{r show.gene_set_test.marginal}
res_zenith_marginal.GO[['Scz']][1:20,] %>% kable(caption="Scz") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.MSigDB[['Scz']][1:20,] %>% kable(caption="Scz") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.GO[['BP']][1:20,] %>% kable(caption="BP") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.MSigDB[['BP']][1:20,] %>% kable(caption="BP") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.GO[['Sex']][1:20,] %>% kable(caption="Sex") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.MSigDB[['Sex']][1:20,] %>% kable(caption="Sex") %>% kable_styling(full_width=FALSE)
```
